A note on multi agent learning

### 2016-06-30 multiAgentLearning/paper/article.tex
with parameters

\section{Satisficing play in action}
\todo{make an intermezzo of this?}
\toReview
To demonstrate a potential use of this algorithm we will use at several example
cases. The first one being the iterated prisoner's dilemma.
\fbox{
  \begin{minipage}{2.5in}
    \toReview
    \subsection{A prisoner's dillema introduction}
    The prisoner's dillema is one of the classical game theory examples.
    Consider the following normal form game which is a prisoner's dillema:
    \begin{tabular}{lll}
                & Cooperate   & Defect \\
      Cooperate & $(2,2)$     & $(0,3)$  \\
      Defect    & $(3,0)$     & $(1,1)$  \\
    \end{tabular}
    The Nash equilibrium of this game lies on (Defect,Defect). However, all but
    that action are pareto optimal actions. So the Nash equilibrium would be the
    ``right'' strategy to play if the game is only played once. However if you repeat
    the game against the same opponent you can ``solve''
    the prisoner's dilemma, meaning not playing the Nash equilibrium,
    but trying to get pareto optimal rewards. This
    is often done by starting defecting as soon as your opponent starts
    defecting, both the tit for tat and win stay lose shift strategies do this.
  \end{minipage}
}
\toReview Strategies such as tit for tat or win stay lose shift already know
which actions are winning and which are punishing to try and solve it.
Satisficing play learns this however by updating the aspiration it got from
playing a move. If we consider a game versus always cooperate for example:

@@

In this table we can see satisficing play and tit for tat ending up in a cycle.
at $t=0$ satisficing gained to little reward for its ambition level $\alpha_t$,
and therefore switches action in the next round. In $t=1$ saticificing play
is satisfied, but int $t=2$ it no longer is so it switches but this even ends
up being worse at $t=3$. After that the cycle resets at $t=4$, the cycle becomes
most obvious when looking at the $\pi_t$ column. Also note about this opponent
that if saticificing play would've started with a lower aspiration, it would
not enter this cycle and just keep on cooperating.
\fbox{
  \begin{minipage}{2.5in}
    \toReview
    \subsection{Karandikar's algorithm}
    In the \nameref{sec:core-algorithm} section we said we would use Karandikar's
    notation, but use the simplified version of stimpson.
    Karandikar version would not necessarily change action when being
    disappointed (aspiration level not met), but would switch with a
    probability $p$, which he called \emph{inertia}.

@@

The actual comparison of the algorithms is done by \citep{crandall}, in here
we will discuss several of his results. All the algorithms are compared in self
play. The first game result we'll discuss
is the already introduced prisoner's dillema:
\includegraphics[width=2.5in]{crandall/prisoners}

@@

Shapley's game is a 3 action choice game. If saticificing play has to change
action, instead of picking the other action, it will just pick uniformly random
of the 2 other actions. The context of the game is left to the imagination
of the reader and the normal form game looks like this:

@@

\section{Properties of satisficing play}
\drafting

@@

also showing the contrast graph which supports the work of \citep{arthur}
}
\section{An extended satisficing play}
\drafting

\todo{
In here we discuss the work of \citep{stimpson:2003}, where he extends the
algorithm to be played with mutliple action choices.
Stimpson created a game where resources had to be allocated among agents.
}

>>>>

\section{Satisficing play in action}
\toReview
To demonstrate a potential use of this algorithm we will use at several example
cases. The first one being the iterated prisoner's dilemma.

\noindent
\fbox{
  \begin{minipage}{2.5in}
    \toReview
    \subsection{A prisoner's dillema introduction}
    The prisoner's dillema is one of the classical game theory examples.
    Consider the following normal form game which is a prisoner's dillema:
    \begin{tabular}{lll}
                & Cooperate   & Defect \\
      Cooperate & $(2,2)$     & $(0,3)$  \\
      Defect    & $(3,0)$     & $(1,1)$  \\
    \end{tabular}
    The Nash equilibrium of this game lies on (Defect,Defect). However, all but
    that action are pareto optimal actions. So the Nash equilibrium would be the
    ``right'' strategy to play if the game is only played once. However if you repeat
    the game against the same opponent you can ``solve''
    the prisoner's dilemma, meaning not playing the Nash equilibrium,
    but trying to get pareto optimal rewards. This
    is often done by starting defecting as soon as your opponent starts
    defecting, both the tit for tat and win stay lose shift strategies do this.
  \end{minipage}
}
\toReview Strategies such as tit for tat or win stay lose shift already know
which actions are winning and which are punishing to try and solve it.
Satisficing play learns this however by updating the aspiration it got from
playing a move. If we consider a game versus always cooperate for example:

@@

In this table we can see satisficing play and tit for tat ending up in a cycle.
at $t=0$ satisficing gained to little reward for its ambition level $\alpha_t$,
and therefore switches action in the next round. In $t=1$ saticificing play
is satisfied, but int $t=2$ it no longer is so it switches but this even ends
up being worse at $t=3$. After that the cycle resets at $t=4$, the cycle becomes
most obvious when looking at the $\pi_t$ column. Also note about this opponent
that if saticificing play would've started with a lower aspiration, it would
not enter this cycle and just keep on cooperating.

\noindent
\fbox{
  \begin{minipage}{2.5in}
    \toReview
    \subsection{Karandikar's algorithm}
    In the \nameref{sec:core-algorithm} section we said we would use Karandikar's
    notation, but use the simplified version of stimpson.
    Karandikar version would not necessarily change action when being
    disappointed (aspiration level not met), but would switch with a
    probability $p$, which he called \emph{inertia}.

@@

The actual comparison of the algorithms is done by \citep{crandall}, in here
we will discuss several of his results. All the algorithms are compared in self
play. The algorithms use the following parameters:

\begin{tabular}{ll}
  Satisficing & $\alpha_0\in \mathbb{P}_0, \lambda=0.99$ \\
  WoLF-PHC & $\lambda=1/(10+0.001 k^a_s), \gamma = 0.95, \epsilon-\text{greedy w}$ 
             $/\epsilon = \tex{max}(0.2-0.0006t,0)$ \\
\end{tabular}

The first game result we'll discuss
is the already introduced prisoner's dillema:
\includegraphics[width=2.5in]{crandall/prisoners}

@@

Shapley's game is a 3 action choice game. The context of the game is left to
the imagination of the reader and the normal form game looks like this:

@@

\noindent
\fbox{
  \begin{minipage}{2.5in}
    \drafting
    \subsection{Multi-action saticificing}
    In their paper \citep{stimpson:2003} introduce a modification to
    saticificing play.
    Rather than just picking the other action, which it can't do because there
    are more than that available, it will pick uniformly across the other
    actions. This change allows saticificing play to play in $n$-action games
    rather than just 2 action games.
  \end{minipage}
}

The multi-agent social dillema (MASD) was invented by \citep{stimpson:2003}. This game
is impossible to express in normal form, since it consists of $N$ players (well
it is possible if $N=2$, but otherwise not really).
Each player has a choice of allocating $M$ units to either his own goal, 
or the group goal. The Nash equilibrium of this game lies when all agents
contribute all of the resources towards their own goal. But the Nash bargaining
solution lies on contributing everything towards to group goal. We will present
the results of \citep{crandall}, since \citep{stimpson:2003} didn't do bar-charts,
although they also compared against Q-Learning and came towards similar results:

\includegraphics[width=2.5in]{crandall/masd}

In here we can see saticificing play outperforming Q-Learning and WoLF quite
starkly. But we can also see that this result looks quite a lot like the
prisoners dillema result. This is because the MASD was basically a generalization
of the prisoners dillema, so this result isn't surprising.

\section{Properties of satisficing play}
To analyse saticfing play further we use the work of \citep{karandikar} and
\citep{stimpson:2001}. Karandikar gave some good theoretical foundations,
whereas stimpson did some deep emepircal experiments on self play in the
prisoners dillema with parameter perturbations.
\drafting

@@

also showing the contrast graph which supports the work of \citep{arthur}
}
